Fourmile

### 2022-08-02 fourmile_dataprocess.Rmd
differencing between gages

library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
```

@@

@@

@@

@@

precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
  theme_bw() +
  ggtitle('Daily precip')

@@

#look at 2011-2013
precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
   scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
  theme_bw() +
  ggtitle('Daily precip')

ggplotly(precip_datelim)

#monthly sums
monthlyp <- daily_p %>%
  group_by(site, year(date), month(date)) %>%
  summarize(precip_mo_mm = sum(precip_mm, na.rm=T),
            mo_yr = median(date))

mo_precip <- ggplot(monthlyp, aes(mo_yr, precip_mo_mm, color=site)) + geom_col(position ='dodge') +
  scale_x_date(limits = as.Date(c('2012-06-01', '2014-01-01'))) +
  ggtitle('Precip - monthly sum') + theme_bw()

ggplotly(mo_precip)

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
```

@@

## Gage locations

USGS2 and DS2 have the same coordinates. USGS1 and DS3 have the same coordinates.

```{r map, echo=FALSE}
locations <- read_csv(here('data', 'Outlets.csv'))

locations <- locations %>%
st_as_sf(., coords=c('y','x'), crs = 4326)

mapview(locations, zcol = 'name')

@@

Notes on gages: So far DS2 and DS3 have not been used. US1 and DS1 are mostly point measurements.

@@

## Streamflow differencing from USGS1 (outlet)

```{r hydrographs_diff, echo=F}
#streamflow differencing
q_diff <- daily_q %>%
  pivot_wider(names_from = site, values_from = q_m3s) %>%
  mutate(usgs2_diff = usgs1 - usgs2,
         us1_diff = usgs1 - us1,
         ds1_diff = usgs1 - ds1,
         ds2_diff = usgs1 - ds2,
         ds3_diff = usgs1 - ds3) %>%
  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')

diff <- ggplot(q_diff, aes(x=date, y=q_m3s, color=site)) + 
  geom_line() +
  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
  ylim(-1.1,0.6) +
  theme_bw() + 
  ggtitle('Daily streamflow difference from USGS1')

ggplotly(diff)

#streamflow percent
# q_percent <- daily_q %>%
#   pivot_wider(names_from = site, values_from = q_m3s) %>%
#   mutate(usgs2_diff = usgs2 / usgs1,
#          us1_per = us1 / usgs1,
#          ds1_per = ds1 / usgs1,
#          ds2_per = ds2 / usgs1,
#          ds3_per = ds3 / usgs1) %>%
#   select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
#   pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
# 
# percent <- ggplot(q_percent, aes(x=date, y=q_m3s*100, color=site)) + 
#   geom_line() +
#   labs(y='percent of USGS1') +
#   ylim(0,1125) +
#   scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
#   theme_bw() + 
#   ggtitle('Daily streamflow percent of USGS1') 
# 
# ggplotly(percent)

## Streamflow differencing between each gage

DS1 minus US1 (uppermost)

```{r DS1-US1, echo=FALSE}

diff_ds1 <- daily_q %>%
  pivot_wider(names_from = site, values_from = q_m3s) %>%
  mutate(ds1_us1 = ds1 - us1) %>%
  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')

diff1 <- ggplot(diff_ds1, aes(x=date, y=q_m3s)) + 
  geom_point() +
  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
  #ylim(-1.1,0.6) +
  theme_bw() + 
  ggtitle('Daily streamflow DS1 - US1')

ggplotly(diff1)

mean(diff_ds1$q_m3s, na.rm=T)

USGS2 minus DS1

```{r USGS2-DS1, echo=FALSE}

diff_usgs2 <- daily_q %>%
  pivot_wider(names_from = site, values_from = q_m3s) %>%
  mutate(usgs2_ds1 = usgs2 - ds1) %>%
  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')

diff2 <- ggplot(diff_usgs2, aes(x=date, y=q_m3s)) + 
  geom_point() +
  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
  #ylim(-1.1,0.6) +
  theme_bw() + 
  ggtitle('Daily streamflow USGS2 - DS1')

ggplotly(diff2)

mean(diff_usgs2$q_m3s, na.rm=T)

USGS1 - USGS2

```{r USGS1-USGS2, echo=FALSE}
diff_usgs1 <- daily_q %>%
  pivot_wider(names_from = site, values_from = q_m3s) %>%
  mutate(usgs2_ds1 = usgs1 - usgs2) %>%
  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')

diff3 <- ggplot(diff_usgs1, aes(x=date, y=q_m3s)) + 
  geom_point() +
  scale_x_date(limits = as.Date(c('2011-01-01', '2013-12-01'))) +
  #ylim(-1.1,0.6) +
  theme_bw() + 
  ggtitle('Daily streamflow USGS1 - USGS2')

ggplotly(diff3)

mean(diff_usgs1$q_m3s, na.rm=T)

@@

precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
  theme_bw() +
  ggtitle('Daily precip (Gordon N and S)')

@@

# #look at 2011-2013
# precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
#    scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
#   theme_bw() +
#   ggtitle('Daily precip (2011-2013)')
# 
# ggplotly(precip_datelim)

#monthly sums
# monthlyp <- daily_p %>%
#   group_by(site, year(date), month(date)) %>%
#   summarize(precip_mo_mm = sum(precip_mm, na.rm=T),
#             mo_yr = median(date))
# 
# mo_precip <- ggplot(monthlyp, aes(mo_yr, precip_mo_mm, color=site)) + geom_col(position ='dodge') +
#   scale_x_date(limits = as.Date(c('2012-06-01', '2014-01-01'))) +
#   ggtitle('Precip - monthly sum') + theme_bw()
# 
# ggplotly(mo_precip)
